A pipeline to analyse time-course gene expression data

### 2019-05-13 scripts/manuscript.Rmd
a few more changes

`moanin` provides a simple interface to perform a time by time differential
expression analysis. Under the hood, it simply calls `limma` [@ritchie:limma] on the set of
contrasts provided. Here, we show an example between the control mouse and the
mouse infected with the high dose of the influenza strain A/Vietnam/1203/04
(H5N1), but the function works with any form contrasts.

>>>>

`moanin` provides a simple interface to perform a timepoint by timepoint differential
expression analysis. This is traditionally done by the user defining the comparisons (called `contrasts` in linear models).  Under the hood, simply calls `limma` [@ritchie:limma] on the set of
contrasts provided. **EAP: Can we comment on using it for RNA-Seq??**

Here, we show an example where we define our contrasts to be the difference between the control mouse ("M") and the
mouse infected with the high dose of the influenza strain A/Vietnam/1203/04
(H5N1) ("VL") for each time point, but the function works with any form contrasts. **FIXME: Reference to limma vignette for how to define the contrasts** **EAP: Could you make simple function that creates them automatically for two conditions -- i.e. find union of time points for two conditions... Then we could show an example with just a couple done manually, and then say we can also use a little helper function in the `moanin` that will do it for all time points**
